---
title: "Week 7.1 - Open Science Project"
author: "Lucas Peinado Bruscato"
date: "22/01/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Open Science Project

## Q1) theoretical hypothesis

Average rating for Adam Sandler movies are equal to the average rating for Ryan Gosling movies, comparing the last 25 movies they had performed. Will only be considered movies that weren't classified as "TV Series", "TV Movie", "Short", "Video short" or when appears "uncredited" about the performance of the actor in the movie.

## Q2) dependent variables

I will compare the ratings over the movies both actors performed and I will use a null-hypothesis significance testing (NHST), given I expect there will be a significant difference.

## Q3) justify your sample size

All the analysis will be done using 50 observations because this are the only data available for the hypothesis given.

## Q4) specify the statistical test you will conduct

I will use:

- alpha level equals to 3%
- one-sided test
- statistical power of 90%

```{r}

library(dplyr)
library(pwr)

# read dataset
dataset <- read.csv('../Importable Data/Week_7_1_database.csv', ';', header = TRUE)

head(dataset)

# disable scientific notation
options(scipen = 999)

# number of lines
dataset %>% 
  nrow()

# calculate average rating for adam sandler movies
adamSandlerAvg <- (dataset %>% 
  filter(actor == "Adam Sandler") %>% 
  select(rating) %>% 
  summarise(avg = mean(rating)))$avg

adamSandlerAvg

# calculate average rating for ryan gosling movies
ryanGoslingAvg <- (dataset %>% 
  filter(actor == "Ryan Gosling") %>% 
  select(rating) %>% 
  summarise(avg = mean(rating)))$avg

ryanGoslingAvg

# calculate standard deviation of all dataset
sd <- (dataset %>% 
  select(rating) %>% 
  summarise(sd = sd(rating)))$sd

# hypothesis testing for difference between averages
t.test(dataset %>% 
         filter(actor == 'Ryan Gosling') %>% 
         select(rating),
       mu = adamSandlerAvg)

# as we can see, the p-value is very low so the null hypothesis can be rejected

pwr.t.test(d = (adamSandlerAvg - ryanGoslingAvg)/sd,
           n = 55,
           sig.level = 0.03,
           type = "one.sample",
           alternative = "two.sided")$power

# in that manner, the statistical power is very high

```

## Q5) relevant statistics

As expected, the results where statistically significant cause the differences are high (assuming that one knows a little bit about movies rating).




